Antigenic phenotypes and phylogenetic metrics improve forecasts of seasonal influenza A/H3N2 evolution

### 2019-12-11 manuscript/main.tex
Include notes to self and update provisional manuscript title

We fit models to these simulated populations using all sequence-only fitness metrics.
As a positive control for our model framework, we also fit a model based on the true fitness of each sample as measured by the simulator.
We evaluated the performance of each model by the absolute distance between projected and observed future populations and how often it outperformed a naive model that estimated no change in populations between years.
As each model only projects existing sequences forward one year without trying to predict which mutations occur in the future, the model's absolute distance to the future can never be zero.
For this reason, we additionally measured how well each model approximated the diversity of the future population.
We measured this approximation at each timepoint as the average Hamming distance between projected and observed populations minus the average Hamming distance of the observed population to itself.

@@

\begin{itemize}
\item{Our model accurately forecasts clade frequency trajectories and identifies optimal potential vaccine strains for both simulated and natural populations by estimating the sequence composition of future populations and without relying on clade-based model targets}
\item{Experimental measurements of antigenic drift based on HI assays are more predictive of viral success than epitope mutations}
\item{The combination of sequence-only metrics outperforms all experimentally-informed metrics}
\item{Deleterious mutations contribute more to seasonal influenza evolution than has been as widely appreciated}
\item{DMS measurements appear to be too background-specific to be predictive for global viral success}
\item{Further efforts to understand the declining efficacy of HI assays and to replace these with FRA or antigenic escape assays could improve models in the future}
\item{Our model live forecasts in nextstrain.org will aid in year-round surveillance of influenza evolutionary patterns and allow us to continuously evaluate model performance relative to recent observations}
\item{Our model is the first of its kind to be released as an open source framework that can be inspected and extended by others}
\item{Immediate next steps to improve influenza models under this framework include the integration of geographic information and antigenic escape assay data}
\item{Our distance-based model targets and easy definition of fitness metrics through tidy data frames paves the way for future forecasting efforts with pathogens that cannot be analyzed by standard phylogenetic methods (e.g., highly recombinant viruses and organisms with larger genomes like bacteria and fungi)}
\end{itemize}

>>>>

We fit models to these simulated populations using all sequence-only fitness metrics.
As a positive control for our model framework, we also fit a model based on the true fitness of each sample as measured by the simulator.
We evaluated the performance of each model by the absolute distance between projected and observed future populations and how often it outperformed a naive model that estimated no change in populations between years.
As each model only projects existing sequences forward one year without trying to predict which mutations occur in the future, the model's absolute distance to the future can never be zero.
For this reason, we additionally measured how well each model approximated the diversity of the future population.
We measured this approximation at each timepoint as the average Hamming distance between projected and observed populations minus the average Hamming distance of the observed population to itself.
%% Insert summary statistics of future diversity without describing average Hamming distance
%% and remove approximation of future diversity text.

@@

\begin{itemize}
\item{Our model accurately forecasts clade frequency trajectories and identifies optimal potential vaccine strains for both simulated and natural populations by estimating the sequence composition of future populations and without relying on clade-based model targets}
\item{Experimental measurements of antigenic drift based on HI assays are more predictive of viral success than epitope mutations}
\item{Models based on a predefined set of epitope sites risk overfitting to historical data}
\item{The combination of sequence-only metrics outperforms all experimentally-informed metrics across validation data but fails to account for reassortment events in test data}
\item{Deleterious mutations contribute more to seasonal influenza evolution than has been as widely appreciated}
\item{DMS measurements appear to be too background-specific to be predictive for global viral success}
\item{Further efforts to understand the declining efficacy of HI assays and to replace these with FRA or antigenic escape assays could improve models in the future}
\item{Our model live forecasts in nextstrain.org will aid in year-round surveillance of influenza evolutionary patterns and allow us to continuously evaluate model performance relative to recent observations}
\item{Our model is the first of its kind to be released as an open source framework that can be inspected and extended by others}
\item{Immediate next steps to improve influenza models under this framework include the integration of geographic information and antigenic escape assay data}
\item{Our distance-based model targets and easy definition of fitness metrics through tidy data frames paves the way for future forecasting efforts with pathogens that cannot be analyzed by standard phylogenetic methods (e.g., highly recombinant viruses and organisms with larger genomes like bacteria and fungi)}
\end{itemize}
